# Overview/Executive Summary

*In this section we describe the dataset and summarizes the goal of the project and key steps that were performed.*
      
This project is part of the Capstone of the Professional Certificate Program of Data Science and it has as scope applying machine learning techniques that go beyond standard linear regression, giving the opportunity to use a publicly available dataset to solve the problem of your choice. The [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/index.php) and [Kaggle](https://www.kaggle.com/datasets) are good places to seek out a dataset.

For this project, the [Cardiac Arrhythmia](https://archive.ics.uci.edu/ml/datasets/Arrhythmia) dataset from UCI Machine Learning Repository was selected. As we can guess this is a life/health dataset and as the web page mention, this dataset has the following main information:

* This database contains 279 attributes, 206 of which are linear valued and the rest are nominal.

* Concerning the study of H. Altay Guvenir: "The aim is to distinguish between the presence and absence of cardiac arrhythmia and to classify it in one of the 16 groups. Class 01 refers to 'normal' ECG classes 02 to 15 refers to different classes of arrhythmia and class 16 refers to the rest of unclassified ones. For the time being, there exists a computer program that makes such a classification. However there are differences between the cardiolog's and the programs classification. Taking the cardiolog's as a gold standard we aim to minimise this difference by means of machine learning tools." 





```{r Overview Download & Initial Setup, include = FALSE}
##########################################################
# Download & Setup
##########################################################

# Note: this process could take a couple of minutes

if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table)) install.packages("data.table", repos = "http://cran.us.r-project.org")
#if(!require(kableExtra)) install.packages("kableExtra")  # does not works in Linux
if(!require(gmodels)) install.packages('gmodels')
if(!require(rpart)) install.packages('rpart')
if(!require(randomForest)) install.packages('randomForest')
if(!require(e1071)) install.packages('e1071')
if(!require(rpart.plot)) install.packages("rpart.plot")

library(tidyverse)
library(caret)
library(data.table)
#library(kableExtra) # does not works in Linux
library(gmodels)
library(rpart)
library(randomForest)
library(e1071) # SVM
library(xml2) #Kable
library(rpart.plot)


source(file="CrossTableNarrow.R") # Minor change in Column and Row Total Headings of gmodels::CrossTable
# To use KableExtra works in linux
#source(file="../kableExtra/R/add_header_above.R") 
#source(file="../kableExtra/R/util.R")
#source(file="../kableExtra/R/from_knitr.R")
source(file="../kableExtra/R/kable_styling.R") # to center table
source(file="../kableExtra/R/scroll_box.R")
source(file="../kableExtra/R/util.R")
source(file="../kableExtra/R/magic_mirror.R") # kable latex


# Cardiac Arrhythmia dataset:
# https://archive.ics.uci.edu/ml/datasets/Arrhythmia
# https://archive.ics.uci.edu/ml/machine-learning-databases/arrhythmia/arrhythmia.data



arrhythmia.uci <- read.csv(url("https://archive.ics.uci.edu/ml/machine-learning-databases/arrhythmia/arrhythmia.data"),
                     header=FALSE,
                     stringsAsFactors = FALSE)


colnames(arrhythmia.uci)[280] <- "Class code"


# Set NA to the ? value (missing value)
arrhythmia.uci[arrhythmia.uci == "?"] <- NA
```

## Characteristics of dataset
The Arrhythmia dataset is a table witch each row it is collection of health measurement for one patience and the last column says if this persons it is a normal health or has some of the 15 arrhythmia.


```{r Overview Characteristics of dataset,size=10}
# dimension
dim(arrhythmia.uci)
# Display predictors (columns)
str(arrhythmia.uci, list.len = 25)
```

You can see there are few patients but a lot of elements to consider. This elements are displayed as the first view we can see that required some work in setting its proper name (provided in the description of the dataset) but we are not to cover each one because we are talking of 279 predictors.



```{r Overview Class definition, include = FALSE}

Class <- data.frame(`Class code`= 01, `Class name` = "Normal", check.names = FALSE)
Class <- bind_rows( Class,
                    data.frame(`Class code`= 02, `Class name` = "Ischemic changes (Coronary Artery Disease)", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 03, `Class name` = "Old Anterior Myocardial Infarction", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 04, `Class name` = "Old Inferior Myocardial Infarction", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 05, `Class name` = "Sinus tachycardy", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 06, `Class name` = "Sinus bradycardy", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 07, `Class name` = "Ventricular Premature Contraction (PVC)", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 08, `Class name` = "Supraventricular Premature Contraction", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 09, `Class name` = "Left bundle branch block", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 10, `Class name` = "Right bundle branch block", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 11, `Class name` = "1. degree AtrioVentricular block", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 12, `Class name` = "2. degree AV block", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 13, `Class name` = "3. degree AV block", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 14, `Class name` = "Left ventricule hypertrophy", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 15, `Class name` = "Atrial Fibrillation or Flutter", check.names = FALSE))
Class <- bind_rows( Class,
                    data.frame(`Class code`= 16, `Class name` = "Others", check.names = FALSE))
Class$`Class code` <- as.factor(Class$`Class code`)
```


About the output, the last column give us the Class code. 1 is for "Normal" and all the rest are arrhythmia. First we are going to display de distribution in a table, where you can see that "Normal" take a preponderance percentage and later a graph where we can see how the different arrhythmia are distributed in our dataset


```{r Overview class as factor, include = FALSE}
# Initial Redefine some type of the predictor from initial read from files. if using R 3.6 or earlier:
arrhythmia <- arrhythmia.uci %>% mutate(`Class code` = as.factor(`Class code`)
                                        )
```


```{r Overview Class code table, echo=FALSE, message=FALSE}
left_join(arrhythmia, Class, by = "Class code") %>% 
  group_by(`Class code`, `Class name`) %>% summarise( "N Ocurrences" = n(), Percentage = round(100*n()/nrow(arrhythmia),digits = 1)) %>%
  knitr::kable(caption = "Presence of codes in our dataset")
  
```

You can see than some arrhythmias type are not present in our dataset (11, 12 and 13).

```{r Overview Distribution of Cardiac Arrhythmia Class, echo=FALSE, warning=FALSE}
left_join(arrhythmia, Class, by = "Class code") %>% ggplot(aes(`Class name`)) + geom_histogram(stat="count") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))  + # Rotate axis labels
  xlab("Cardiac Arrhythmia Classification") +
  ylab("Number of Patiences with the Disease") +
  ggtitle("Class Distribution of Cardiac Arrhythmia Dataset")
```


## Approach
The develop of this predicting Cardiac Arrhythmia classification can be explained in the follows steps:

1.- Start analyzing the dataset, cleaning, working on missing values that we found, look for outsider than can be invalid data, review predictors that does not add value and define the outcomes that we are going to predict.

2.- Create the training and validation, or test, dataset.

3.- Works with several classification supervised machines to get a better accuracy in our predictions. Evaluate sensitivity and specificity.

4.- Review the results.

5.- Conclusion.



\newpage
